### 2022-02-01 manuscript/manuscript.Rmd
Update manuscript.Rmd

```{r generaltopicsfig, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 6.5, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}
plot_any_dedicated_joint + plot_all_topics + plot_annotation(tag_levels = 'A') &
  theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(size = 14, hjust = 0, vjust = 0))
```

>>>>

```{r generaltopicsfig, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 6.5, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}
plot_any_dedicated_joint + plot_all_topics + plot_annotation(tag_levels = 'A') &
  theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(size = 14, hjust = 0, vjust = 0))

# to save individual plots for twitter
# ggsave(plot = plot_any_dedicated_joint, file = here('manuscript','figs','twitter','fig1A.png'), width = 6, height = 6.5, units = "in", dpi = 300)
# ggsave(plot = plot_all_topics, file = here('manuscript','figs','twitter','fig1B.png'), width = 6, height = 6.5, units = "in", dpi = 300)
```
